Reviewer Comments (Scientific Reports)

### 2020-03-24 notebook/sci_rep_reviews.Rmd
Make small edits to the response to Reviewer 3's comments

Theoretical studies of community stability assign negative diagonal values (typically -1) to make the simplifying assumption that components of the system are self-regulating (e.g., May 1972, 1973; Sinha 2005; Allesina and Tang 2012; Grilli et al. 2017; Song and Saavedra 2018; Stone 2018). If individual components are not self-regulating, then the system will almost never be stable. I tried this very early on in the process of investigating the effects of $\gamma$ by allowing diagonal elements to be sampled in the same way as off-diagonals: from a normal distribution centred at zero (data are here, note that the tables show the information in a bit more of a confusing format that in the SI, which was subsequently improved prior to my original submission: https://github.com/bradduthie/RandomMatrixStability/blob/dfe6f8e0225733c94348bc9e0dad6218c59cc109/notebook/sim_results_old/oldest/mat_dat.csv). The effect of $\gamma$ on increasing stability is retained, but stability of all systems drops to zero out of one million given size $S > 14$. And in the random systems that are found to be stable, all diagonal elements are nearly always negative (or, rarely, with one or two very low positive values). In other words, if diagonal elements were randomly sampled from a distribution with positive support, then the only systems that would be stable would be those that by chance had all (or nearly all) negative diagonal elements.

@@

Unequal diagonal elements could be used, but doing so would only be expected to add some variation around the expected centre of eigenvalue distributions, and would not change my primary result concerning the effect of $\gamma$ (note that this would lead to the same results as mentioned above where diagonal elements were sampled in the same way as off diagonals, but with more total stable systems since the mean diagonal value would be less lower).

>>>>

Theoretical studies of community stability assign negative diagonal values (typically -1) to make the simplifying assumption that components of the system are self-regulating (e.g., May 1972, 1973; Sinha 2005; Allesina and Tang 2012; Grilli et al. 2017; Song and Saavedra 2018; Stone 2018). If individual components are not self-regulating, then the system will almost never be stable. I tried this very early on in the process of investigating the effects of $\gamma$ by allowing diagonal elements to be sampled in the same way as off-diagonals: from a normal distribution centred at zero (data are here, note that the tables show the information in a bit more of a confusing format that in the SI, which was subsequently improved prior to my original submission: https://github.com/bradduthie/RandomMatrixStability/blob/dfe6f8e0225733c94348bc9e0dad6218c59cc109/notebook/sim_results_old/oldest/mat_dat.csv). The effect of $\gamma$ on increasing stability is retained, but the stability of all systems drops to zero out of one million given size $S > 14$. And in the random systems that are found to be stable, all diagonal elements are nearly always negative (or, rarely, with one or two very low positive values). In other words, if diagonal elements were randomly sampled from a distribution with positive support, then the only systems that would be stable would be those that by chance had all (or nearly all) negative diagonal elements.

@@

Unequal diagonal elements could be used, but doing so would only be expected to add some variation around the expected centre of eigenvalue distributions, and would not change my primary result concerning the effect of $\gamma$ (note that this would lead to the same results as mentioned above where diagonal elements were sampled in the same way as off diagonals, but would result in more variation in the mean diagonal value, d).
